\documentclass[a4paper, twoside]{report}
\input{preamble.tex}

\title{Tank Commander Mixed Reality Simulation}
\author{Marat (Matt) Sadykov}

\begin{document}
\input{title/title.tex}

\begin{abstract}
The project described in this report is aimed to provide an overview of a simulation tank commander game over a year of work.
It includes some project definitions used in the semester one Progress Report and builds on top of the same report from semester two.
It also provides additional possibilities, which may open a new investigation area for other researchers, such as parallelising specific jobs using the NVIDIA CUDA Library. \\     
The goal is to develop a Mixed Reality (MR) simulation, linked to $1/16^{th}$ scaled tank model, which is controlled by a wireless joystick and connected to $360\circ$ constantly streaming camera. Video output is meant to be processed inside the Unity Game Engine, enabling additional computational possibilities.
Using Unity Environment to create a Virtual World, an entirely new simulation will present a uniquely immersive experience of the tank commander.
The camera, located on top of the tank, will help reconstruct the surrounding environment and detect potential targets using a certain degree of Machine Learning (ML). \\[1pt]
In addition to MR implementation, the project aims to investigate the full potential of Unity environment processing abilities in Object Detection and improve performance with CUDA Library and additional TensorFlow processing.
With its Machine Learning (ML) model, Game Engine should be capable of identifying opponents tanks.
As a potential possibility, the project may set new goals for other developers to wait until specific progress is made in innovation and build on top of it.
The goal of the final product was simplified to bring an immersive first-person single-player tank commander game using Augmented Reality (AR) in a close-quarters arena.
\end{abstract}

% \renewcommand{\abstractname}{Acknowledgements}
% \begin{abstract}
% It is usual to thank those individuals who have provided particularly useful assistance, technical or otherwise, during your project.
% \textbf{Additional features:}
% \textbf{InvokeRepeat and Cancel Repeat., Taking scrennshot in particular resolution. Canvas in VR. Adapted tank from Rodney. LED acted according to direction.}
% \textbf{TODO: Add mechanincs of mving. ROtationg turret and shooting. Train ML model}
% \end{abstract}

\tableofcontents
\listoffigures
%\listoftables
\input{introduction/introduction.tex}
\input{background/background.tex}
\input{project/project.tex}
\input{evaluation/evaluation.tex}
\input{conclusion/conclusion.tex}

\bibliographystyle{unsrt}
%\bibliographystyle{referencing/IEEEtran}
\bibliography{referencing/referenceList}
\addcontentsline{toc}{chapter}{Bibliography}

\input{appendix/appendix.tex}

\end{document}